air4children: Artificial Intelligence and Robotics for Children

### 2021-03-02 slides/main.tex
polishes main slide

\title{air4children: Artificial Intelligence and Robotics for Children}
%\subtitle{...}
\author{
R. Montenegro,
E. Corona,
A. Mandujano,
D. Badillo-Perez,
D. Cruz,
{\bf Miguel Xochicale}
}
\date{
Workshop Child-Robot Interaction \& Child's Fundamental Rights at \faHashtag HRI2021\\
March 08, 2021
}
\institute{
    \faTwitter @air4children  \faGithubAlt @air4children
	\faEnvelope air4children@gmail.com
		}

\titlegraphic{
  \begin{tikzpicture}[overlay, remember picture]
    \node[%
      above right=0.35cm and -0.2cm of current page footer area.south west,
      anchor=south west,
      inner sep=0pt] {%
      \usebeamerfont{footline}
      \begin{tabular}{lm{.8\textwidth}}
        \href{http://creativecommons.org/licenses/by/4.0/}{\ccby} &
        This slices is licensed under a
	\href{http://creativecommons.org/licenses/by/4.0/}
		{Creative Commons ``Attribution 4.0 International''} license. 
	\par Get source of this slides and see further references 
		from \url{https://github.com/air4children/hri2021}.
      \end{tabular}
    };
    \node[%
      above left=0.35cm and 0cm of current page footer area.south east,
      anchor=south east,
      inner sep=0pt]{\qrcode[height=1.5cm]{https://github.com/mxochicale/}};
  \end{tikzpicture}
}

>>>>

\title{air4children: Artificial Intelligence and Robotics for Children}
%\subtitle{...}
\author{
R. Montenegro,
E. Corona,
D. Badillo-P\'erez,
A. Mandujano,
D. Cruz,
{\bf Miguel Xochicale}
}
\date{
Workshop Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
March 08, 2021
}
\institute{
	\faEnvelope   air4children@gmail.com \\
	\faGithubAlt @air4children \faTwitter @air4children  
		}

\titlegraphic{
  \begin{tikzpicture}[overlay, remember picture]
    \node[%
      above right=0.35cm and -0.2cm of current page footer area.south west,
      anchor=south west,
      inner sep=0pt] {%
      \usebeamerfont{footline}
      \begin{tabular}{lm{.8\textwidth}}
        \href{http://creativecommons.org/licenses/by/4.0/}{\ccby} &
        This slices is licensed under a
	\href{http://creativecommons.org/licenses/by/4.0/}
		{Creative Commons ``Attribution 4.0 International''} license. 
	\par Get source of this slides and see further references 
		from \url{https://github.com/air4children/hri2021}.
      \end{tabular}
    };
    \node[%
      above left=0.35cm and 0cm of current page footer area.south east,
      anchor=south east,
      inner sep=0pt]{\qrcode[height=1.5cm]{https://github.com/air4children/hri2021}};
  \end{tikzpicture}
}
